Categorical Predictor Embeddings in Actuarial Modeling

### 2021-04-02 manuscript/manuscript.Rmd
occupancy type pic

For Model 2, the neural network with one-dimensional embeddings, the task is simple: we can simply plot the levels
on a line, as in Figure \@ref(fig:num-floors). In the case of `flood_zone`, since we happen to have the luxury of knowing a
priori the meaning of the prefixes, we can plot them separately, as in Figure \@ref(fig:flood-zone) to see how the model 
mapped them.

```{r num-floors, echo=FALSE, fig.cap="Number of floors", out.width = "80%", fig.align="center"}
knitr::include_graphics("images/num_floors.png")
```

>>>>

For Model 2, the neural network with one-dimensional embeddings, the task is simple: we can simply plot the levels
on a line, as in Figure \@ref(fig:occ-type). In the case of `flood_zone`, since we happen to have the luxury of knowing a
priori the meaning of the prefixes, we can plot them separately, as in Figure \@ref(fig:flood-zone) to see how the model 
mapped them.

```{r occ-type, echo=FALSE, fig.cap="Occupancy type", out.width = "80%", fig.align="center"}
knitr::include_graphics("images/occupancy_type.png")
```
